Digital Analysis of Paintings

### 2014-05-07 paper.tex
Add paper 14

>>>>

Chinese calligraphy is a painted art in its own right, although not exactly
like a painted scene it does provide some insight into stroke extraction which
has a much more formalised ground truth.

\cite{xu2005automatic} described a method for the automatic extraction of
calligraphy strokes, with account for differing stroke sizes, deformations and
noise found in historical work.

Unlike paintings, Chinese calligraphy is only comprised of a certain catalogue
of strokes and are categorised into either basic or composed strokes.

The input, a binary image, has the Canny edge detection
algorithm\cite{canny86computational} performed on it to extract the edge of the
character.

Because calligraphy strokes often overlap, the corner points of the edges of
the character are found preserving information about the direction this process
was performed in.

A half-edge colouring graph can be created to show the relations between
different edges. Each edge is split into two half-edges which has colours
according to the relation to other edges. This information, plus the direction
information allows the computation of matching different edges to build a
single stroke, with relation to the distances of different vertices.

This is done by removing the largest edge then trying to find one or more edges
which can match to it to make a stroke. Once the stroke is found it can then
have the gaps filled in by linking the two nearest vertices.

There is little experimentation and no formal validation performed other than a
visual check. The authors even note an occurrence where the corner detection
algorithm failed to provide reasonable vertices and so the strokes had to be
extracted manually.

One would have though in an area where it would be easy to generate a ground
truth, it would have been used to at least perform some form of statistical
analysis on the results gained.

This might be useful in edge cases of digitally analysing paintings, but
without knowing how well it truly performs on calligraphy, one might be
hesitant to apply this to a what is a much more complex field which needs the
consideration of colour as opposed to a binary intensity.

Whilst there are claims this technique should be able to cope with noise from
historical degradation of the image, it is difficult to see how. Especially as
Canny is known to susceptible to noise and can be improved to be less
sensitive\cite{xiao10improved}.
